{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-04-09 FH Optimality Conditions Paper.tex
some further changes
subplots and more details on diff wrt lambda

%\documentclass[preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\input{paperPreamble}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\begin{document}

@@

It is immediately clear that, the $\ch_2(t_f)$-error satisfies 
\begin{equation}\label{merexp}
\begin{aligned}
%\scalemath{0.9}
{
\norm{\h-\h_r}_{\ch_2({\tf})}^2=\norm{\h}_{\ch_2({\tf})}^2-2 \langle\h, \h_r\rangle_{\ch_2({\tf})}+\norm{\h_r}_{\ch_2({\tf})}^2,
}
\end{aligned}
\end{equation}
where the inner product  $\langle\h, \h_r\rangle_{\ch_2({\tf})}$ is real since $\h(t)$ and $\h_r(t)$ are real. Finding the first-order necessary conditions for optimal ${\ch_2({\tf})}$ model reduction will require computing the gradient of the error expression \eqref{merexp} with respect to the optimization variables. 
Since the reduced model, as described by  the impulse response in $\h_r(t)$, is parametrized by the 
reduced order poles $\{\lambda_i\}$, and the residue directions $\{\lc_i\}$ and $\{\rc_i\}$, we will be computing the gradient of the error with respect to these variables. Since the first term in the error \eqref{merexp}, i.e., $\norm{\h}_{\ch_2({\tf})}$, is a constant, we will be focusing on the remaining two terms only. First, in the next lemma, we will formulate these two last terms in terms of $\{\lambda_i\}$, 
$\{\lc_i\}$ and $\{\rc_i\}$.
\begin{Lemma}\label{minnerexp}

@@

 Let $\J$ denote the $\ch_2({\tf})$ error norm square, i.e., 

@@

\lc_k^T\G(-\lambda_k)=\lc_k^T\G_r(-\lambda_k) \quad \mbox{and}\quad
\G(-\lambda_k)\rc_k=\G_r(-\lambda_k)\rc_k,

@@

After some tedious manipulations, we obtain 

@@

\begin{dmath}\label{eqn:l1} 
\pder[\J]{\lambda_k} =-2\lc_k^T \left(\sum_{j=1}^n \cc_j\bb_j^T \dfrac{({\tf}(\lambda_k+\rho_j)-1)e^{(\rho_j+\lambda_k){\tf}}+1}{(\lambda_k+\rho_j)^2}\right)\rc_k  
+2\lc_k^T \left(\sum^r_{i=1} \lc_i\rc_i^T\dfrac{({\tf}(\lambda_i+\lambda_j\k)-1)e^{(\lambda_i+\lambda_k){\tf}}+1}{(\lambda_i+\lambda_k)^2}\right)\rc_k.

@@

%\end{aligned}
%\end{equation}
Lemma \eqref{mgexp}, specifically \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk}, show that the expressions in the parentheses in \eqref{eqn:l1}  are, respectively, $-\G'(-\lambda_k)$ and $-\G_r'(-\lambda_k)$.
If $\pder[\J]{\lambda_k}= 0$, then
\lc_k^T\G'(-\lambda_k)\rc_k&=\lc_k^T\G_r'(-\lambda_k)\rc_k,
which completes the proof.
\begin{flushright} $\Box$  \end{flushright}
{\color{red} We note that the interval of interest is problem dependent and the choice of the interval i.e. the choice of $t_f$ may depend on the model, however, these optimality conditions hold for any choice of $t_f>0$.}

@@

  \begin{figure}[H] 
 \centering
 \includegraphics [scale=0.4]{allDataHeatF} 
 \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
 \end{figure}
 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.4]{ErrorVSrISSF}
 \caption{\FH \ and other algorithms for the ISS model \label{fig:iss}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.4]{ErrorVSrUNSF}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
 \end{figure}

>>>>

%\documentclass[preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\input{paperPreamble}

%to avoid whitespace
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}

\begin{document}

@@

It is immediately clear that, the $\ch_2(t_f)$-error, denoted by $\J$, satisfies 
\begin{equation}\label{merexp}
\begin{aligned}
\J&=\norm{\h-\h_r}_{\ch_2({\tf})}^2\\
&=\norm{\h}_{\ch_2({\tf})}^2-2 \langle\h, \h_r\rangle_{\ch_2({\tf})}+\norm{\h_r}_{\ch_2({\tf})}^2,
\end{aligned}
\end{equation}
where the inner product  $\langle\h, \h_r\rangle_{\ch_2({\tf})}$ is real since $\h(t)$ and $\h_r(t)$ are real. Finding the first-order necessary conditions for optimal ${\ch_2({\tf})}$ model reduction will require computing the gradient of the error expression \eqref{merexp} with respect to the optimization variables. 
Since the reduced model, as described by  the impulse response in $\h_r(t)$, is parametrized by the 
reduced order poles $\{\lambda_i\}$, and the residue directions $\{\lc_i\}$ and $\{\rc_i\}$, we will be computing the gradient of the error with respect to these variables. Since the first term in the error \eqref{merexp}, i.e., $\norm{\h}_{\ch_2({\tf})}$, is a constant, we will be focusing on the remaining two terms only. First, in the next lemma, we will formulate these two last terms in terms of $\{\lambda_i\}$, 
$\{\lc_i\}$ and $\{\rc_i\}$.
\begin{Lemma}\label{minnerexp}

@@

 As mentioned above, let $\J$ denote the $\ch_2({\tf})$ error norm square, i.e., 

@@

\lc_k^T\G(-\lambda_k)&=\lc_k^T\G_r(-\lambda_k), \\ %\quad \mbox{and}\quad
\G(-\lambda_k)\rc_k&=\G_r(-\lambda_k)\rc_k,

@@

@@

\begin{dmath}\label{eqn:diffl}
\pder[\J]{\lambda_k}=-2\lc_k^T \left(\sum_{j=1}^n \cc_j\bb_j^T \dfrac{{\tf}(\lambda_k+\rho_j)e^{(\rho_j+\lambda_k){\tf}}} {(\lambda_k+\rho_j)^2}     -\dfrac       {e^{(\rho_j+\lambda_k){\tf}}-1}{(\lambda_k+\rho_j)^2}\right)\rc_k 
+2\lc_k^T \left(\sum^r_{i=1} \lc_i\rc_i^T\dfrac{{\tf}(\lambda_i+\lambda_j\k)e^{(\lambda_i+\lambda_k){\tf}}}  {(\lambda_i+\lambda_k)^2}         -\dfrac{e^{(\lambda_i+\lambda_k){\tf}}-1}{(\lambda_i+\lambda_k)^2}\right)\rc_k.

@@

We rewrite \eqref{eqn:diffl} to obtain

\begin{dmath}
\pder[\J]{\lambda_k} =-2K_1+2K_2
\end{dmath}
where
\begin{dmath}\label{eqn:l11} 
K_1=\lc_k^T \left(\sum_{j=1}^n \cc_j\bb_j^T \dfrac{({\tf}(\lambda_k+\rho_j)-1)e^{(\rho_j+\lambda_k){\tf}}+1}{(\lambda_k+\rho_j)^2}\right)\rc_k  
\end{dmath}
\begin{dmath}\label{eqn:l12} 
K_2=\lc_k^T \left(\sum^r_{i=1} \lc_i\rc_i^T\dfrac{({\tf}(\lambda_i+\lambda_j\k)-1)e^{(\lambda_i+\lambda_k){\tf}}+1}{(\lambda_i+\lambda_k)^2}\right)\rc_k.
\end{dmath}

%\begin{dmath}\label{eqn:l1} 
%\pder[\J]{\lambda_k} =-2\lc_k^T \left(\sum_{j=1}^n \cc_j\bb_j^T \dfrac{({\tf}(\lambda_k+\rho_j)-1)e^{(\rho_j+\lambda_k){\tf}}+1}{(\lambda_k+\rho_j)^2}\right)\rc_k  
%+2\lc_k^T \left(\sum^r_{i=1} \lc_i\rc_i^T\dfrac{({\tf}(\lambda_i+\lambda_j\k)-1)e^{(\lambda_i+\lambda_k){\tf}}+1}{(\lambda_i+\lambda_k)^2}\right)\rc_k.
%\end{dmath}
%\end{aligned}
%\end{equation}
Lemma \eqref{mgexp}, specifically \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk}, show that the expressions in the parentheses in \eqref{eqn:l11}  and \eqref{eqn:l12}   are, respectively, $-\G'(-\lambda_k)$ and $-\G_r'(-\lambda_k)$.
If $\pder[\J]{\lambda_k}= 0$, then
\begin{align*}
\lc_k^T\G'(-\lambda_k)\rc_k&=\lc_k^T\G_r'(-\lambda_k)\rc_k,
\end{align*}
which completes the proof.
\begin{flushright} $\Box$  \end{flushright}
{\color{red} We note that the interval of interest is problem dependent and the choice of the interval i.e. the choice of $t_f$ may depend on the model, however, these optimality conditions hold for any choice of $t_f>0$.}

@@

 %This is the original figure
%  \begin{figure}[H] 
% \centering
% \includegraphics [scale=0.4]{allDataHeatF} 
% \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
% \end{figure}
% \begin{figure}[H]
% \centering
%  \includegraphics [scale=0.4]{ErrorVSrISSF}
% \caption{\FH \ and other algorithms for the ISS model \label{fig:iss}}
% \end{figure}
%  \begin{figure}[H]
% \centering
%   \includegraphics [scale=0.4]{ErrorVSrUNSF}
%      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
% \end{figure}
%

 \begin{figure}[H] 
 \centering
 \includegraphics [scale=0.4]{fig1} 
 \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
 \end{figure}
 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.4]{fig2}
 \caption{\FH \ and other algorithms for the heat model \label{fig:hm1}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.4]{fig3}
      \caption{\FH \ and other algorithms for the ISS model \label{fig:iss}}
 \end{figure}

 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.4]{fig4}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
 \end{figure}
